Quasi-consistent efficient meshfree thin shell formulation to naturally accommodate essential boundary conditions

### 2024-03-09 response.tex

\documentclass{article}
\usepackage{amsmath,amssymb,amsfonts,amsthm,bm}
\title{Response to Reviewer's Comments}
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}
\begin{document}

\maketitle

The authors sincerely thank the reviewers for their further comments. Accordingly, the authors have meticulously revised the manuscript and the details are given as follows.

\section*{Reviewer \#1}
\textit{This manuscript provides a meshfree thin shell formulation based on the Hu-Washizu variational principle. The essential boundary conditions in the present formulation do not require additional artificial parameters, which can be considered insensitive to those in Nitsche and Penalty’s approaches. The derivation is rigorous however several issues must be properly addressed before the publication. I recommend a major revision.}

\textbf{1.} \textit{After Eq. 5, the formulation of theta needs to be provided.}

\textbf{Reply:}

\textbf{2.} \textit{Consider using different symbols for the mid-surface displacement, v is always referring to velocity.}

\textbf{Reply:} Thanks to reviewer's suggestion. However, the velocity is not involved in this paper, it will not lead any misunstanding as $\boldsymbol v$ is denoted for mid-plane displacement.

\textbf{3.} $\boldsymbol \theta$ \textit{is the variation of $\boldsymbol a_3$, so $\boldsymbol \theta \cdot \boldsymbol a_3=0$. This relationship does not come from $\epsilon_{3i} = 0$, which was in Eq. (9).}

\textbf{Reply:} Thanks, the reviewer is right, the rotation $\boldsymbol \theta$ is perpendicular to $\boldsymbol a_3$. However, this relationship is also equivalent with $\epsilon_{3i}=0$, which follows the Kirchhofff hypothesis.

\textbf{4.} \textit{Eq. (10) seems to be wrong. Where is $\boldsymbol a_{3,\alpha}$ and where is the most complicated term $\boldsymbol \theta_{,\alpha}$?}

\textbf{Reply:} Thank you for this comment. The detailed dervation of Eq. (10) is given by the following steps:
\begin{equation}
    \begin{split}
        \kappa_{\alpha\beta} &=\frac{1}{2}(\boldsymbol a_{3,\alpha} \cdot \boldsymbol v_{,\beta} + \boldsymbol v_{,\alpha} \cdot \boldsymbol a_{3,\beta} + \boldsymbol a_\alpha \cdot \boldsymbol \theta_{,\beta} + \boldsymbol \theta_{,\alpha} \cdot \boldsymbol a_\beta) \\
        &=\frac{1}{2} \left ( 
        \begin{split}
            &\underbrace{(\boldsymbol a_3 \cdot \boldsymbol v_{,\beta})_{,\alpha} - \boldsymbol a_3 \cdot \boldsymbol v_{,\alpha\beta}}_{\boldsymbol a_{3,\alpha} \cdot \boldsymbol v_{,\beta}} \\
            +&\underbrace{(\boldsymbol a_3 \cdot \boldsymbol v_{,\alpha})_{,\beta} - \boldsymbol a_3 \cdot \boldsymbol v_{,\alpha\beta}}_{\boldsymbol v_{,\beta} \cdot \boldsymbol a_{3,\alpha}} \\
            -& \boldsymbol a_\alpha \cdot \underbrace{((\boldsymbol v_{,\gamma} \cdot \boldsymbol a_3)_{,\beta} \boldsymbol a^\gamma + \boldsymbol v_{,\gamma} \cdot \boldsymbol a_3 \boldsymbol a^\gamma_{,\beta})}_{-\boldsymbol \theta_{,\beta}} \\
            -& \boldsymbol a_\beta \cdot \underbrace{((\boldsymbol v_{,\gamma} \cdot \boldsymbol a_3)_{,\alpha} \boldsymbol a^\gamma + \boldsymbol v_{,\gamma} \cdot \boldsymbol a_3 \boldsymbol a^\gamma_{,\alpha})}_{-\boldsymbol \theta_{,\alpha}} \\
        \end{split}
        \right ) \\
        &=\frac{1}{2} \left ( 
        \begin{split}
            &\underbrace{(\boldsymbol a_3 \cdot \boldsymbol v_{,\beta})_{,\alpha}
            +(\boldsymbol a_3 \cdot \boldsymbol v_{,\alpha})_{,\beta}
            -(\boldsymbol v_{,\alpha} \cdot \boldsymbol a_3)_{,\beta}
            -(\boldsymbol v_{,\beta} \cdot \boldsymbol a_3)_{,\alpha}}_{0} \\
            -&2\boldsymbol a_3 \cdot \boldsymbol v_{,\alpha\beta}
            - \boldsymbol v_{,\gamma} \cdot \boldsymbol a_3 \underbrace{\boldsymbol a_\alpha \cdot \boldsymbol a^\gamma_{,\beta}}_{-\Gamma_{\alpha\beta}^\gamma}
            - \boldsymbol v_{,\gamma} \cdot \boldsymbol a_3 \underbrace{\boldsymbol a_\beta \cdot \boldsymbol a^\gamma_{,\alpha}}_{-\Gamma_{\alpha\beta}^\gamma} \\
        \end{split}
        \right ) \\
        &= (\Gamma_{\alpha\beta}^\gamma \boldsymbol v_{,\gamma} - \boldsymbol v_{,\alpha\beta}) \cdot \boldsymbol a_3
    \end{split}
\end{equation}
The detailed derivation can be found in reference (Benzaken et al. 2021). For the conciseness, the detailed derivation of Eq. (10) is not listed in manuscript, and the related statement has been added on line 150 (Page ).

\textbf{5.} \textit{Patchtest: table 2 is interesting. Eq. (62) assumes the solution is only polynomials on the mid-surface, which is already not a polynomial in the Cartesian coordinate. The flat model is simple, in this case, the parametric domain is the same as Cartesian. I believe the error in the curved case is due to bad parametrization. In general, the solution should be able to reproduce the parametric polynomials if the integration and parametrization are both good.}

\textbf{Reply:} Thank you for your comment. As we can find in Eqs. (32), (33), (35), (36),  the proposed approach was designated for polynomial strains and stresses. For flat model, the polynomial displacement leads to the polynomial strains and stresses. However, for curved model, the only polynomial strains can be got, the stresses turn to be non-polynomial due to the curvilinear coordinates. As a result, even the integration and parametrization are well posed, the approximated smoothed stresses cannot exactly reproduce this non-polynomial stresses. That is why the approach was named with "quasi-consistent".

\textbf{6.} \textit{Example 5.2, figure (7) is distracting. The purpose of the newly designed method is to get rid of the penalty parameters. In general, the final penalty parameter should be $E/h\times C$, where $C$ is a dimensionless coefficient. If one is testing the convergence rate of Nitsche or penalty methods, the penalty parameter needs to be scaled by the mesh size $h$, when the model is refined.}

\textbf{Reply:}

\textbf{7.} \textit{In Example 5.2, the authors provided the wrong reference value. $-0.3024$ is the one under RM shell theory. In this case, I believe the value should be $-0.3006$. See [1] for more information.}

\textbf{Reply:} Thank you for your suggestion, the reference value has been changed to $-0.3006$. Accordingly, the related statement on Page 21 is modified.

\textbf{8.} \textit{In Example 6.2, also check if the reference value provided in this study is for RM shells [2].}

\textbf{Reply:}

\textbf{9.} \textit{Scodelis-Lo roof, pinched hemisphere, and pinched cylinder are the most famous shell benchmark problems. In [3], the authors named them ”shell obstacle course”. These 3 examples are even harder than those finite deformation shell simulations. So a good shell formulation should be capable of passing these three challenges. It is strongly suggested that the authors add the pinched cylinder simulation to this manuscript.}

\textbf{Reply:}

\section*{Reviewer \#2}
\textit{With the aid of the Hu-Washizu variational principle and reproducing kernel smoothed gradients, an efficient and quasi-consistent meshfree Galerkin method is presented in this manuscript to solve thin shell problems. An outstanding merit of the method is that the essential boundary conditions can be enforced naturally. Computational formulas of the method are presented with some details. Numerical results are given to demonstrate the efficiency of the method.}

\textit{The current manuscript is well presented and contains material worthy of publication. Acceptance of the manuscript is recommended. The authors are, however, encouraged to address the comments listed below.}

\textbf{1.} \textit{Please check the gramma of the sentence below Eq. (22).}

\textbf{Reply:} Thanks, following the suggestion, this sentence have been revised on Page 9 and the authors have also doubly checked the writing of this revised.

\textbf{2.} \textit{Why is only the quadratic function used for the basis function vector p in Eq. (23)?}

\textbf{Reply:} Thanks for this comment, following the suggestion, this sentence have been revised on Page 9 and the authors have also doubly checked the writing of this revised.

\textbf{3.} \textit{Please provide the meaning of the symbol $s_{\alpha I}$ in Eq. (25). What is the parameter value used in this paper?}

\textbf{Reply:} Thanks for this comment, following the suggestion, this sentence have been revised on Page 9 and the authors have also doubly checked the writing of this revised.

\textbf{4.} \textit{Fig. 2 contains two sets of integration points. Considering the computational burden, using only one set of integration points may be more beneficial for Galerkin meshfree methods. Therefore, it is recommended to provide some explanations.}

\textbf{5.} \textit{On page 13, the authors stated that "Even with p-th order variational consistency, the proposed formulation can not exactly reproduce the solution spanned by basis functions". The reproducibility is important for Galerkin meshfree methods. So, just suggestion, is it possible to give some more explicit explanations.}

\textbf{6.} \textit{Numerical results of Nitsche's method and penalty method are also shown in Section 5.1. The values of penalty parameters used in the two methods should be provided. In addition, it is encouraged to provide some observations on numerical results of the RKGSI-penalty in Figure 4 and Tables 1 and 2.}

\textbf{7.} \textit{On pages 32-34, some reference information such as journal title and year of publication is missed.}

\textbf{Reply:} Thanks a lot, following the reviewer's suggestion, these reference's information have been revised, the authors also have doubly checked all the information and formats of references.

\end{document}

### 2024-03-09 examples.tex
20240309

\section{Numerical examples}
In this section, several examples are carried out to verify proposed method, which employs the consistent reproducing kernel gradient smoothing integration scheme (RKGSI) and the non-consistent Gauss integration scheme (GI) with penalty method, Nitsche's method and the proposed Hu-Washizu formulation (HW) to enforce the essential boundary conditions. A normalized support size of 2.5 is used for all methods to ensure the requirement of quadratic base meshfree approximation. To eliminate the influence of integration, the Gauss integration scheme use 6 Gauss points for domain integration and 3 points for boundary integration, and such that the number of integration points are identical between Gauss scheme and RKGSI scheme. The error estimates of displacement namely $L_2$-Error and energy namely $H_e$-Error is used here:
\begin{equation}
\begin{split}
L_2\text{-Error} &= \frac{\sqrt{\int_\Omega(\boldsymbol v - \boldsymbol v^h) \cdot (\boldsymbol v - \boldsymbol v^h)d\Omega}}{\sqrt{\boldsymbol v \cdot \boldsymbol v}} \\
H_e\text{-Error} &= \frac{\sqrt{\int_\Omega \left ((\varepsilon_{\alpha\beta} - \varepsilon_{\alpha\beta}^h)(N^{\alpha\beta} - N^{\alpha\beta h}) + \int_\Omega(\kappa_{\alpha\beta}-\kappa_{\alpha\beta}^h)(M^{\alpha\beta}-M^{\alpha\beta h}) \right )d\Omega}}{\sqrt{\int_\Omega(\varepsilon_{\alpha\beta}N^{\alpha\beta} + \kappa_{\alpha\beta}M^{\alpha\beta})d\Omega}}
\end{split}
\end{equation}

\subsection{Patch tests}
The linear and quadratic patch tests for flat and curved thin shell are firstly study to verify the variational consistency of the proposed method. As shown in Fig. \ref{ptf1}, the flat and curved model is depicted by an identical parametric domain $\Omega = (0,1)\otimes(0,1)$, where the cylindrical coordinate system with radius $R=1$ is employed to describe the curved model, and the whole domain $\Omega$ is discretized by $165$ meshfree nodes. All the boundaries are enforced as essential boundary conditions with the following manufactured exact solution:
\begin{equation}
\boldsymbol v = \begin{Bmatrix}
(\xi^1+2\xi^2)^n \\ (3\xi^1+4\xi^2)^n \\ (5\xi^1+6\xi^2)^n
\end{Bmatrix},\quad
n = \begin{cases}
1 & \text{Linear patch test} \\
2 & \text{Quadratic patch test}
\end{cases}
\end{equation}

\begin{figure}[h!]
    \centering
    \includegraphics[width=\textwidth]{figures/patchtest_msh}
    \caption{Meshfree discretization for patch test}\label{ptf1}
\end{figure}

Table \ref{ptt1} lists the $L_2$- and $H_e$-Error results of patch test with flat model, where the RKGSI with variational consistent essential boundary enforcement, i.e. RKGSI-Nitsche and RKGSI-HW, can pass the linear and quadratic path test. Due to the loss of variational consistency condition, even with Nitsche's method, Gauss meshfree formulations show noticeable errors. Table \ref{ptt2} shows the results for curved model, which indicated that all the mehtods cannot pass the patch test, which mainly because the proposed smoothed gradient of Eqs. (\ref{approxse1}), (\ref{approxse2}) is unable to exactly reproduce the non-polynomial membrane and bending stress. However, the RKGSI-HW and RKGSI-Nitsche also performance better accuracy than other methods due to the fulfillment of first two order variational consistency. Meanwhile, the bending moment contours of $M^{12}$ are listed in Fig. \ref{ptf2}, which further verify that the proposed method obtain a satisfactory result comparing with exact solution, the conventional Gauss meshree formulations show observable errors.

\begin{table}[h!]
\centering
\caption{Results of patch test for flat model}\label{ptt1}
\begin{tabular}{lcccc}
\toprule
 & \multicolumn{2}{c}{Linear patch test} & \multicolumn{2}{c}{Quadratic patch test} \\ \cline{2-5}
 & $L_2$-Error & $H_e$-Error & $L_2$-Error & $H_e$-Error \\
    \midrule
    GI-Penalty & $4.45E-4$ & $1.35E-2$ & $2.01E-3$ & $1.63E-2$ \\
    GI-Nitsche & $4.51E-4$ & $1.42E-2$ & $1.22E-3$ & $1.68E-2$ \\
    RKGSI-Penalty & $3.64E-9$ & $6.77E-8$ & $4.54E-9$ & $6.57E-8$ \\
    RKGSI-Nitsche & $3.31E-12$ & $1.34E-11$ & $5.98E-12$ & $1.21E-11$ \\
    RKGSI-HR & $6.67E-13$ & $1.50E-11$ & $1.07E-12$ & $1.26E-11$ \\
    \bottomrule
\end{tabular}
\end{table}

\begin{table}[h!]
\centering
\caption{Results of patch test for curved model.}\label{ptt2}
\begin{tabular}{lcccc}
\toprule
 & \multicolumn{2}{c}{Linear patch test} & \multicolumn{2}{c}{Quadratic patch test} \\ \cline{2-5}
 & $L_2$-Error & $H_e$-Error & $L_2$-Error & $H_e$-Error \\
    \midrule
    GI-Penalty & $3.79E-4$ & $1.30E-2$ & $1.74E-3$ & $1.37E-2$ \\
    GI-Nitsche & $4.04E-4$ & $1.42E-2$ & $1.15E-3$ & $1.49E-2$ \\
    RKGSI-Penalty & $1.47E-4$ & $5.39E-3$ & $2.26E-4$ & $2.09E-3$ \\
    RKGSI-Nitsche & $2.41E-6$ & $7.37E-5$ & $2.47E-6$ & $2.89E-5$ \\
    RKGSI-HR & $4.28E-6$ & $1.30E-4$ & $9.69E-6$ & $2.41E-4$ \\
    \bottomrule
\end{tabular}
\end{table}

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{figures/patchtest_msh}
\caption{Contour plots of $M^{12}$ for curved shell patch test.}\label{ptf2}
\end{figure}

\subsection{Scordelis-Lo roof}
This example consider the classical Scordelis-Lo roof problem, as shown in Fig., the cylindrical roof has the radius $R=25$, length $L=50$, thickness $h=0.25$, Young's modulus $E=4.32\times 10^8$ and Poisson rate $\nu=0.0$. An uniform body force of $b_z = -90$ are enforced in whole roof and the curved edges are enforced by $v_x=v_z=0$, and the straight edges are free.

Due to the symmetry, only a quadrant of the model is considered for meshfree analysis, which is discretized by the $5\times 8$, $11\times 16$, $17\times 24$ and $23\times32$ meshfree nodes.

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{figures/patchtest_msh}
\caption{Description of Scordelis-Lo roof problem.}\label{ptf2}
\end{figure}

>>>>

\section{Numerical examples}\label{examples}
The suggested method, which uses Nitsche's method, the consistent reproducing kernel gradient smoothing integration scheme (RKGSI), and the non-consistent Gauss integration scheme (GI) with penalty method, as well as the proposed Hu-Washizu formulation (HW) to enforce the necessary boundary conditions, is validated in this section through several examples. A normalized support size of 2.5 is used for all the methods to ensure the requirement of quadratic base meshfree approximation. To eliminate the influence of integration, the Gauss integration scheme uses 6 Gauss points for domain integration and 3 points for boundary integration, so as to maintain the same integration accuracy between domain and boundaries. Moreover, the number of integration points are identical between the Gauss and RKGSI schemes. The error estimates of displacement ($L_2$-Error) and energy ($H_e$-Error) is used here:
\begin{equation}
\begin{split}
L_2\text{-Error} &= \frac{\sqrt{\int_\Omega(\boldsymbol v - \boldsymbol v^h) \cdot (\boldsymbol v - \boldsymbol v^h)d\Omega}}{\sqrt{\boldsymbol v \cdot \boldsymbol v}} \\
H_e\text{-Error} &= \frac{\sqrt{\int_\Omega \left ((\varepsilon_{\alpha\beta} - \varepsilon_{\alpha\beta}^h)(N^{\alpha\beta} - N^{\alpha\beta h}) + \int_\Omega(\kappa_{\alpha\beta}-\kappa_{\alpha\beta}^h)(M^{\alpha\beta}-M^{\alpha\beta h}) \right )d\Omega}}{\sqrt{\int_\Omega(\varepsilon_{\alpha\beta}N^{\alpha\beta} + \kappa_{\alpha\beta}M^{\alpha\beta})d\Omega}}
\end{split}
\end{equation}

\subsection{Patch tests}
The linear and quadratic patch tests for flat and curved thin shells are firstly studied to verify the variational consistency of the proposed method. As shown in Fig. \ref{ptf1}, the flat and curved models are depicted by an identical parametric domain $\Omega = (0,1)\otimes(0,1)$, where the cylindrical coordinate system with radius $R=1$ is employed to describe the curved model, and the whole domain $\Omega$ is discretized by the $165$ meshfree nodes. All the boundaries are enforced as essential boundary conditions with the following manufactured exact solution:
\begin{equation}
\boldsymbol v = \begin{Bmatrix}
(\xi^1+2\xi^2)^n \\ (3\xi^1+4\xi^2)^n \\ (5\xi^1+6\xi^2)^n
\end{Bmatrix},\quad
n = \begin{cases}
1 & \text{Linear patch test} \\
2 & \text{Quadratic patch test}
\end{cases}
\end{equation}

\begin{figure}[!ht]
    \centering
    \includegraphics[width=\textwidth]{figures/ptmsh}
    \caption{Meshfree discretization for patch test}\label{ptf1}
\end{figure}

Table \ref{ptt1} lists the $L_2$- and $H_e$-Error results of patch test with flat model, where the RKGSI scheme with variational consistent essential boundary enforcement, i.e. RKGSI-Nitsche and RKGSI-HW, can pass the linear and quadratic patch test. Due to the loss of variational consistency condition, even with Nitsche's method, Gauss meshfree formulations show noticeable errors. Table \ref{ptt2} shows the results for curved model, which indicated that all the considered methods cannot pass the patch test. This is mainly because the proposed smoothed gradient of Eqs. (\ref{approxse1}) and (\ref{approxse2}) could not exactly reproduce the non-polynomial membrane and bending stress. However, the RKGSI-HW and RKGSI-Nitsche methods also provide better accuracy compared to others due to the fulfillment of first second-order variational consistency. Meanwhile, the bending moment contours of $M^{12}$ are listed in Fig. \ref{ptf2}, which further verify that the proposed method provided a satisfactory result compared to exact solution. On the other hand, the conventional Gauss meshree formulations showed errors.

\begin{table}[!ht]
\centering
\caption{Results of patch test for flat model.}\label{ptt1}
\begin{tabular}{lcccc}
\toprule
 & \multicolumn{2}{c}{Linear patch test} & \multicolumn{2}{c}{Quadratic patch test} \\ \cline{2-5}
 & $L_2$-Error & $H_e$-Error & $L_2$-Error & $H_e$-Error \\
    \midrule
    GI-Penalty & $4.45E-4$ & $1.35E-2$ & $2.01E-3$ & $1.63E-2$ \\
    GI-Nitsche & $4.51E-4$ & $1.42E-2$ & $1.22E-3$ & $1.68E-2$ \\
    RKGSI-Penalty & $3.64E-9$ & $6.77E-8$ & $4.54E-9$ & $6.57E-8$ \\
    RKGSI-Nitsche & $3.31E-12$ & $1.34E-11$ & $5.98E-12$ & $1.21E-11$ \\
    RKGSI-HR & $6.67E-13$ & $1.50E-11$ & $1.07E-12$ & $1.26E-11$ \\
    \bottomrule
\end{tabular}
\end{table}

\begin{table}[!ht]
\centering
\caption{Results of patch test for cylindrical model.}\label{ptt2}
\begin{tabular}{lcccc}
\toprule
 & \multicolumn{2}{c}{Linear patch test} & \multicolumn{2}{c}{Quadratic patch test} \\ \cline{2-5}
 & $L_2$-Error & $H_e$-Error & $L_2$-Error & $H_e$-Error \\
    \midrule
    GI-Penalty & $3.79E-4$ & $1.30E-2$ & $1.74E-3$ & $1.37E-2$ \\
    GI-Nitsche & $4.04E-4$ & $1.42E-2$ & $1.15E-3$ & $1.49E-2$ \\
    RKGSI-Penalty & $1.47E-4$ & $5.39E-3$ & $2.26E-4$ & $2.09E-3$ \\
    RKGSI-Nitsche & $2.41E-6$ & $7.37E-5$ & $2.47E-6$ & $2.89E-5$ \\
    RKGSI-HR & $4.28E-6$ & $1.30E-4$ & $9.69E-6$ & $2.41E-4$ \\
    \bottomrule
\end{tabular}
\end{table}

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{figures/ptc}
\caption{Contour plots of $M^{12}$ for curved shell patch test.}\label{ptf2}
\end{figure}

\subsection{Scordelis-Lo roof}
This example considers the classical Scordelis-Lo roof problem, as depicted in Fig. \ref{slf1}. The cylindrical roof has dimensions $R=25$, $L=50$, $h=0.25$, Young's modulus $E=4.32\times 10^8$ and Poisson's ratio $\nu=0.0$. The entire roof is subjected to an uniform body force of $b_z = -90$, with the straight edges remainning free and the the curved edges are enforced by $v_x=v_z=0$.

Due to the symmetry, only a quadrant of the model is considered for meshfree analysis, which is discretized by the $11\times 16$, $13\times 20$, $17\times 24$ and $19\times28$ meshfree nodes, as listed in Fig. \ref{slf2}. The comparison of the displacement in $z-$direction at node $A$, $v_{A3}$, is used as the investigated quantity, with the reference value 0.3024 given by \cite{macneal1985}. Firstly, Fig. \ref{slf3} presents a sensitivity study for the artificial parameters of $\alpha_v$'s, $\alpha_\theta$'s in the RKGSI meshfree formulations with Nitsche's method and penalty method. The results of Fig. \ref{slf3} revealed, Nitsche's method observed less artificial sensitivity. However, both the methods cannot trivially determine the optimal values of the artificial parameters. The optimal artificial parameters from Fig. \ref{slf3} are adopted for the convergence study in Fig. \ref{slf4}. The convergence result showed that the RKGSI get satisfactory results while the traditional Gauss methods demonstrated noticeable errors.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\textwidth]{figures/slm}
\caption{Description of Scordelis-Lo roof problem.}\label{slf1}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{figures/slmsh}
\caption{Meshfree discretizations for Scordelis-Lo roof problem.}\label{slf2}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{figures/sla}
\caption{Sensitivity comparison of $\alpha_v$ and $\alpha_\theta$ for Scordelis-Lo problem.}\label{slf3}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{figures/sld}
\caption{Displacement convergence for Scordelis-Lo roof problem.}\label{slf4}
\end{figure}

\subsection{Pinched Hemispherical shell}
Consider the hemispherical shell shown in Fig. \ref{phf1}, which is loaded at four points $P=\pm 2$ at $90^\circ$ interval at its bottom. The hemispherical shell has an radius $R=10$, thickness $h=0.04$, Young's modulus $E=6.825\times10^7$ and Poisson's ratio $\nu = 0.3$.

Due to symmetry, only quadrant model, where the $8\times8$, $16\times16$, $24\times24$ and $32\times32$ meshfree nodes have been discretized, was considered. The quantity under investigation for convergence is the displacement at $x-$direction on point $A$, $v_{A1}$.
Fig. \ref{phf2} displays the corresponding convergence results, indicating the RKGSI scheme performed significantly better compared to the GI meshfree formulation. Meanwhile, the efficiency comparison for this problem is also shown in Fig. \ref{phf3}, in which the CPU time for assembly and calculation of shape functions are considered. Fig. \ref{phf3}(a) indicates that the RKGSI scheme observed high efficiency in assembly. This is due to the variational inconsistent Gauss meshfree formulation which require more Gaussian points to get satisfactory results. Fig. \ref{phf3}(b) lists the CPU time spent on enforcing essential boundary conditions for the penalty method, Nitsche's method and proposed HW method. The results highlighted that the proposed HW method consumed comparable CPU time in assembly compared to Nitsche's method. However, less time was spent to calculate the shape functions. Since both the HW method and penalty method were developed considering the shape functions first order derivatives. For this reason, both the methods shared an almost identical time in computing the shape functions.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.8\textwidth]{figures/pfm}
\caption{Description of pinched hemispherical shell problem.}\label{phf1}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{figures/pfd}
\caption{Displacement convergence for pinched hemispherical shell problem.}\label{phf2}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{figures/efficient}
\caption{efficiency comparison for pinched hemispherical shell problem: (a) Whole domain; (b) Essential boundaries}\label{phf3}
\end{figure}

### 2024-03-09 introduction.tex
20240309

\section{Introduction}
Thin shell is one of the most frequently used structure in engineering practice, where the thickness of this kind structure is often much smaller than its radius. With the Kirchhoff-Love hypothesis [1–3], the transverse shear deformation is eliminated in thin shell analysis, such that at least C1 continuous shape functions are required within Galerkin methods. In static and dynamic simulation of structure, the conventional finite element methods [1,2] are one of the most popular approximation scheme, however the construction of C1 continuity is still a big challenge for cell-based finite element methods. In last three decades, the meshfree methods [1–3] equipped high order smoothed shape functions have attracted significant research attention, while the meshfree shape functions are established based upon a set of scattered nodes and the high order continuity of shape functions is easily fulfilled even with low order basis function. For thin shell analysis, this high order meshfree approximations can also alleviate the membrane locking caused by the mismatched approximation order of membrane strain and bending strain [1]. Moreover, in general, the nodal-based meshfree approximations can release the burden of mesh distortion and have the flexibility of local refinement. Due to these advantages, a wide variety meshfree methods are proposed and have been applied to many scientific or engineering fields. Among of them, moving least squares (MLS) and reproducing kernel (RK) meshfree approximations built their shape functions by enforcing the so-call consistency conditions, where the consistency conditions require that the corresponding approximations should exactly reproduce every functions spanned by basis functions, and this conditions usually serve as a basic requirement for the error convergence of resolved Galerkin solutions [1]. However, the high order smoothed meshfree shape functions accompany with the severely overlapping supports, which leads to a misalignment between numerical integration domains and supports of shape functions. As a result, the meshfree shape functions usually exhibit a piecewise rational nature in each integration domains, and it brings a serious difficulty to the accurate numerical integration in Galerkin weak forms [1].

>>>>

\section{Introduction}\label{introduction}
Thin shell structures generally adhere to the Kirchhoff hypothesis \cite{donnell1976}, that neglects the shear deformation can be described using Galerkin formulation which requires to have at least $C^1$ continuity. The traditional finite element methods usually only have $C^0$ continuous shape functions, and it prefers Mindlin thick shear theory, hybrid and mixed models in simulation of shell structure  \cite{hughes2000}. Meshfree methods \cite{belytschko1994,liu1995,chen2017} with high order smoothed shape functions have garnered much research attention over the past thirty years. These techniques established the shape functions based on a collection of dispersed nodes, and the high order continuity of shape functions can be easily achieved even with low-order basis functions. For thin shell analysis, this high order meshfree approximation can also alleviate the membrane locking caused by the mismatched approximation order of membrane strain and bending strain \cite{krysl1996}. Furthermore, nodal-based meshfree approximations generally offer the flexibility of local refinement and can relieve the burden of mesh distortion. Owing to these benefits, numerous meshfree techniques have been developed and implemented in many scientific and engineering fields \cite{liu2009,zhang2000meshless,millan2011,wang2023b,suchde2023,deng2023b}. However, the high order smoothed meshfree shape functions accompany the enlarged and overlapping supports, which may potentially cause many problems for shape functions. One of the issues is the loss of the Kronecker delta property, which means that, unlike the finite element methods, the necessary boundary conditions cannot be directly enforced  \cite{fernandez-mendez2004}. Another issue is that the variational consistency or said integration constraint cannot be satisfied due to the misalignment between the numerical integration domains and supports of shape functions. Besides, the shape functions exhibit a piecewise rational nature in each integration domain. Therefore, variational consistency is vital to the solution accuracy in Galerkin formulations \cite{li2016, wu2021}.

Various ways have been presented to enforce the necessary boundary for Galerkin meshfree methods directly, including the boundary singular kernel method \cite{chen2000a}, mixed transformation method  \cite{chen2000a}, and interpolation element-free method \cite{liu2019a} for recovering shape functions’ Kronecker property. However, these methods are not based on a variational setting and cannot guarantee variational consistency. In the absence of a meshfree node, accuracy enforcement might be poorer. In contrast, enforcing the essential boundary conditions using a variational approach is preferred for Galerkin meshfree methods. The variational consistent Lagrange multiplier approach was initially used to the Galerkin meshfree method by Belytschko et al. \cite{belytschko1994}. In this method, the extra degrees of freedom are used to determine the discretion of Lagrange multiplier. Furthermore, Ivannikov et al. \cite{ivannikov2014a} have extended this approach to geometrically nonlinear thin shells. Lu et al. \cite{lu1994} suggested the modified variational essential boundary enforcement approach and expressed the Lagrange multiplier by equivalent tractions to eliminate the excess degrees of freedom. However, the coercivity of this approach is not always ensured and potentially reduces the accuracy. Zhu and Atluri \cite{zhu1998} pioneered the penalty method for meshfree method, making it a straightforward approach to enforce essential boundary conditions via Galerkin weak form. However, the penalty method lacks variational consistency and requires experimental artificial parameters whose optimal value is hard to determine. Fernández-Méndez and Huerta \cite{fernandez-mendez2004} imposed necessary boundary conditions using Nitsche's approach in the meshfree formulation. This approach can be seen as a hybrid combination of the modified variational method and the penalty method because the modified variational method generates variational consistency through the use of a consistent term, and the penalty method is used as a stabilized term to recover the coercivity. Skatulla and Sansour \cite{skatulla2008} extended Nitsche’s thin shell analysis method and proposed an iteration algorithm to determine artificial parameters at each integration point.

In order to address the issue of numerical integration, a series of consistent integration schemes have been developed for Galerkin meshfree methods. Among these include stabilized conforming nodal integration \cite{chen2001} , variational consistent integration \cite{chen2013}, quadratic consistent integration \cite{duan2012a}, reproducing kernel gradient smoothing integration \cite{wang2019a}, and consistent projection integration  \cite{wang2023}. The assumed strain approach establishes the most consistent integration scheme, while the smoothed gradient replaces the costly higher order derivatives of traditional meshfree shape functions and shows a high efficiency. Moreover, to achieve global variational consistency, a consistent essential boundary condition enforcement should cooperate with the consistent integration scheme. The consistent integration scheme and Nitsche’s method for treating essential boundary conditions show a good performance since they can satisfy the coercivity without requiring additional degrees of freedom. Nevertheless, Nitsche's approach still retains the artificial parameters in stabilized terms, and it is essential to remain conscious of the costly higher order derivatives, particularly for thin plate and thin shell problems. Recently, Wu et al. \cite{wu2022a,wu2023}  proposed an efficient and stabilized essential boundary condition enforcement method based upon the Hellinger-Reissner variational principle, where a mixed formulation in Hellinger-Reissner weak form recasts the reproducing kernel gradient smoothing integration. The terms for enforcing essential boundary conditions are identical to the Nitsche’s method, and both have consistent and stabilized terms. Nevertheless, the stabilized term of this method naturally exists in the Hellinger-Reissner weak form and no longer needs the artificial parameters, even for essential boundary enforcement; instead all of the higher order derivatives are represented by smoothed gradients and their derivatives.

In this study, an efficient and stabilized variational consistent meshfree method that naturally enforces the essential boundary conditions is developed for thin shell structure. Following the concept of the Hellinger-Reissner principle base consistent meshfree method, the Hu-Washizu variational principle of complementary energy with variables of displacement, strains, and stresses is employed. The displacement is approximated by conventional meshfree shape functions, and the strains and stresses are expressed by smoothed gradients with covariant bases. It is important to note that although the first second-order integration requirements are naturally embedded in the smoothed gradients, their fulfillment can only result in a quasi-satisfaction of variational consistency because of the non-polynomial nature of the stresses. Hu-Washizu's weak form is used to evaluate all the essential boundary conditions regarding displacements and rotations. This type of formulation is similar to the Nitsche's method but does not require any artificial parameters. Compared with Nitsche’s method, conventional reproducing smoothed gradients and its direct derivatives replace the costly higher order derivatives. By utilizing the advantages of a replicating kernel gradient smoothing framework, the smoothed gradients showed better performance compared to conventional derivatives of shape functions, hence increasing the meshfree formulation's computational efficiency.

The remainder of this research paper is structured as follows: The kinematics of the thin shell structure and the weak form of the associated Hu-Washizu principle are briefly described in Section 2. Subsequently, the mixed formulation regarding the displacements, strains and stresses in accordance with Hu-Washizu weak form are presented in Section 3. The discrete equilibrium equations are derived in Section 4 using the naturally occurring accommodation of essential, and they are compared to the equations obtained using Nitsche's method. The numerical results in Section 5 validate the efficacy of the proposed Hu-Washizu meshfree thin shell formulation. Lastly, the concluding remarks are presented in Section 6.
